Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
Start on impulsive caption

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Blah Blah}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
  Appendix~\ref{windheat} for a detailed description)).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Most important sources of heating
  after a burst of star formation for $\Mbh=10^6 \Msun$ (top panel)
  and $\Mbh= 10^8 \Msun$ (bottom panel). We also show the velocity
  dispersion from the $\Mbh-\sigma$ relationship as a horizontal gray line
  \citep{Gultekin+09}.}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
  Appendix~\ref{app:windheat} for a detailed description).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}
